My title

### 2024-04-21 paper/paper.qmd
paper updates

raw_data_SPX <- tq_get('SPX',
               from = "1991-07-12",
               to = "2023-03-29",
               get = "stock.prices")

@@

@@

```{r}
SBUX_SPX <-
  cleaned_data_SPX |>
  filter(between(date, as.Date('2023-10-18'), as.Date('2023-11-06')))

class(cleaned_data_SPX$date)

matplot(cleaned_data_SBUX, cbind(cleaned_data_SBUX$Close, cleaned_data_SPX$close), type = "l", lty = 1, 
        col = c("red", "blue"), xlab = "X", 
        ylab = "Y", main = "Multiple Lines Plot")
legend("topright", legend = c("Line 1", "Line 2"), 
       col = c("red", "blue"), 
       lty = 1)
```

@@

starttoendSBUX <- 
  cleaned_data_SBUX |>
  filter(between(Date, as.Date('2023-10-18'), as.Date('2023-11-06')))

kable(starttoendSBUX, 
      col.names = c("Date", 
                    "Closing Stock Price"),
      booktabs = TRUE,
      linesep = ""
)
```

>>>>

raw_data_SPX <- tq_get('SPX',
               from = "1991-07-12",
               to = "2024-03-29",
               get = "stock.prices")

cleaned_data_SPX <-
  raw_data_SPX |>
  select(symbol, date, close)

@@

## Limitations

@@

```{r}
#| label: tbl-SPXandPRKS
#| tbl-cap: Changes in Starbucks Stock Price from One Week Before Legal Action Against Workers United, the the Day it was Announced, to March 28th
#| echo: false

PRKS_SPX <-
  cleaned_data_SPX |>
  filter(between(date, as.Date('2013-07-19'), as.Date('2016-03-16')))

PRKS_Focus <-
  cleaned_data_PRKS |>
  filter(between(Date, as.Date('2013-07-19'), as.Date('2016-03-16')))

SPX_Stocks <- PRKS_SPX$close
PRKS_Stocks <- PRKS_Focus$Close

PRKS_Date <- PRKS_Focus$Date

par(mfrow=c(2,1))
par(mar = c(0, 0, 0, 0))
plot(PRKS_Date,PRKS_Stocks, type="l", col="red" )
plot(PRKS_Date,SPX_Stocks, type="l", col="green" )

@@

twoweeksSBUX <- 
  cleaned_data_SBUX |>
  filter(between(Date, as.Date('2023-10-18'), as.Date('2023-11-06')))

twoweeksSBUX <-
  twoweeksSBUX |> 
  mutate(Difference = Close - lag(Close))

kable(twoweeksSBUX, 
      col.names = c("Date", 
                    "Closing Stock Price",
                    "Difference"),
      booktabs = TRUE,
      linesep = ""
)
```
